---
title: "Git Notes"
format: html
editor: visual
---

## Github Repo for Southsiers Fantasy Football

Southsiders GitHub public repo, <https://github.com/willomi/Southsiders.git>.

### Add Remote in R Studio:

In R Studio, open the Terminal tab (found at the bottom pane).
Run the following command to add the remote repository:

'git remote add origin https://github.com/willomi/Southsiders.git'

### Create a .gitignore File
Create a .gitignore file in the root directory of your R project. This file will specify which files and directories should not be pushed to GitHub.
Example content for .gitignore:

# History files
.Rhistory


# RStudio files
.Rproj.user/

# Specific files to ignore
data/
output/
secrets.txt

### Initialize local repo
Change directory
'cd C:/Users/micha/Football/Southsiders'

Initialize directory
'git init'

If git initializes the directory as the 'master' instead of the 'main' branch, create and switch to the main Branch:
Create a new branch named main and switch to it.
'git checkout -b main'

Add all changed or new files. Dont forget the dot, '.'.
'git add .'

Make initial commit
'git commit -m "Initial commit"'

Push to remote repo
'git push origin main'

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
